%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{0pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{0pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}
\setlist[itemize]{noitemsep, topsep=0pt}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{mail@website.com}\\
	\textbf{{\Large Billy Pak Lam Lee}} & Email : \href{mailto:pl3lee@uwaterloo.ca}{pl3lee@uwaterloo.ca}\\
	\href{https://github.com/pl3lee}{https://github.com/pl3lee} & Mobile : +1(437)224-6179 \\
	& Address: 57 Russell Hill Road, Markham, Ontario, Canada L6C 2M5
\end{tabular*}
%-----------CAREER OBJECTIVE-----------------
% \section{Career Objectives}
% Seeking for a software development internship opportunity that allows me to explore the real-world applications of various CS knowledge learned from University and projects.

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Waterloo}{Ontario, Canada}
{Honours Bachelor of Mathematics - Third Year}{Sep. 2020 -- Aug. 2024}
%   \resumeItemListStart
% %   {Relevenant Courses: Designing Functional Programs, Elementary Algorithm Design and Data Abstraction, Data Types and Structures, Logic and Computation, Introduction to Computers and Computer Systems, Object-Oriented Software Development}
%   \resumeItemListEnd
\begin{itemize}
	\item Cumulative GPA: 3.9/4.0
	\item Double Major: Computational Mathematics and Combinatorics \& Optimization
	\item Minor: Computer Science
\end{itemize}
% \resumeSubheading
%   {Niagara Christian Collegiate}{Ontario, Canada}
%   {Class of 2020;  Cumulative Average: 94}{Sep. 2018 -- June. 2020}
\resumeSubHeadingListEnd
%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart


\resumeSubheading
{Rhetoricon, University of Waterloo}{Waterloo, Ontario, Canada}
{Full Stack Developer Intern (Part-time)}{Jan 2023 - Apr 2023}
\resumeItemListStart
\resumeItem{Rhetoricon Website}
{\begin{itemize}
		\item Contributed in the development of a Next.js and TypeScript frontend and a Golang REST API backend for a cognitive linguistic research group's website
		\item Created responsive and intuitive interfaces using NextJS components and Material UI.
		\item Utilized GitLab pipeline for testing and linting to ensure optimal website performance and maintain high code quality.
		\item Streamlined development processes by transitioning the front-end framework from Ant Design to Material-UI.
		\item Created a backend endpoint that dissociates an instance with a figure.


	\end{itemize}}
\resumeItemListEnd

\resumeSubheading
{\href{https://hanabusa-realty.com/}{Hanabusa Japan Real Estate}}{Japan (Remote)}
{Data Entry Automator}{Sep 2020 - Sep 2021}
\resumeItemListStart
\resumeItem{\href{https://github.com/pl3lee/Hanabusa-Automation}{Web Scraping and Data Entry Automation, Residential Properties}}
{\begin{itemize}
		\item Extracted residential property information and images from a Japanese real estate website (homes.co.jp) using BeautifulSoup4 and entered them into the company website (hanabusa-realty.com) using Selenium in Python.
		\item Saved up to 60 hours of manual labor per month.
	\end{itemize}}
% \resumeItem{\href{https://github.com/pl3lee/Reins-Automation}{Web Scraping, Investment Properties}}
% {\begin{itemize}
% 		\item Extracted investment property information from a Japanese investment property website (system.reins.jp).
% 		\item Wrote a Python script that converted PDF files (Information taken from the website) into HTML files. Then, Selenium was used to select essential property information (over 30 fields) from the HTML file.
% 		\item Saved up to 60 hours per month when compared to manually extracting information.
% 	\end{itemize}}
\resumeItemListEnd



% \resumeSubheading
%   {Lucena Research}{Atlanta, GA}
%   {Data Scientist}{Summer 2012 and 2013}
%   \resumeItemListStart
%     \resumeItem{Portfolio Management}
%       {Created models for portfolio hedging,  portfolio optimization and price forecasting. Also creating a strategy backtesting engine used for simulating and backtesting strategies.}
%     \resumeItem{QuantDesk}
%       {Python backend for a web application used by hedge fund managers for portfolio management.}
%   \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{\href{https://github.com/pl3lee/Biquadris}{Biquadris - C++}}
{\begin{itemize}
		\item Developed a customizable Tetris game variant with adjustable board dimensions and win conditions.
		\item Employed the Model-View-Controller (MVC) design pattern for a robust and maintainable architecture.
		\item Utilized the Factory Method design pattern to generate unique block configurations for varying levels.
		\item Leveraged the X Window System to craft an engaging and user-friendly GUI.
	\end{itemize}}
\resumeSubItem{\href{https://github.com/pl3lee/Recipe-App}{Recipe App - Next.js(TypeScript), Node.js, MongoDB, Express}}
{\begin{itemize}
		\item Developed a recipe sharing web application using Next.js, Node.js, Express, and MongoDB, with user authentication and authorization features and the ability for users to save or unsave recipes.
		\item Designed and implemented the user interface using Material UI.
		\item Used the useContext hook to manage global states.
		\item Utilized TypeScript for improved code reliability and type safety.
	\end{itemize}}
\resumeSubItem{\href{https://github.com/pl3lee/cv-project}{CV Generator - HTML/CSS/JavaScript(React)}}
{\begin{itemize}
		\item Created a webpage that generates a CV using React.
	\end{itemize}}
\resumeSubItem{\href{https://github.com/pl3lee/Sudoku}{Sudoku Solver - Python}}
{\begin{itemize}
		\item Implemented using the backtracking algorithm.
	\end{itemize}}

% \resumeSubItem{\href{https://github.com/pl3lee/Battleship}{Battleship - HTML/CSS/JavaScript(React)}}
% {\begin{itemize}
% 		\item Created a Battleship game using React.
% 	\end{itemize}}



\resumeSubItem{{RunSuite - Bash Script}}
{\begin{itemize}
		\item Created a Bash script that checks if a given program matches the output of the given test suite.
	\end{itemize}}
\resumeSubHeadingListEnd








%
%--------PROGRAMMING SKILLS------------
\section{Skills}
\resumeSubHeadingListStart
\item{
            \textbf{Programming Languages}{: Python, JavaScript, TypeScript, Go, C++, C, Bash, HTML, CSS, SQL, Ruby, R, MIPS Assembly, Racket, LaTeX, MATLAB}
            \hfill
      }
\item{
            \textbf{Technologies/Frameworks}{: React, NextJS, Node.js, MongoDB, Netlify, Heroku, Redux Toolkit, Styled Components, MaterialUI, Firebase, Selenium, BeautifulSoup4, Git, npm, Webpack, Linux/Unix, Adobe Photoshop, MS Office Suite}
      }
\resumeSubHeadingListEnd


%-------------------------------------------



\end{document}