%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{fontawesome5}

% Set applicant's personal data for header
\name{Billy Lee}
\address{Markham, Ontario \linebreak Canada}
\contacts{(437) 224-6179 \linebreak \href{mailto:billy.pl.lee@gmail.com}{billy.pl.lee@gmail.com} \linebreak \href{https://billylee.me}{https://billylee.me} \linebreak \href{https://github.com/pl3lee}{\faGithub} \href{https://www.linkedin.com/in/billy-lee-9892a3200/}{\faLinkedin}}

\begin{document}

	% Print the header
	\makeheader
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Lead Developer / DevOps Engineer}{University of Waterloo}{Jan -- May 2024}	
			\begin{itemize}
				\item Developed a \textbf{Next.js}-based web platform for a figures of speech research group, enabling user submissions and annotations of figure instances.
				\item Revamped the CI/CD process using \textbf{GitLab pipelines}, \textbf{Docker}, and \textbf{Docker Compose}, automating and accelerating testing, building, and deployment phases, and saving over 30 minutes per deployment.
				\item Established a robust staging environment to streamline testing and quality assurance, ensuring a more reliable and efficient development workflow.
				\item Hosted weekly stand-up meetings, conducted code reviews for merge requests, and set up a documentation site with a CD pipeline to ensure proper project documentation.
			\end{itemize}	
		\end{cvsubsection}
		\begin{cvsubsection}{Full Stack Developer}{University of Waterloo}{Jan -- Apr, Sept -- Dec 2023}
			\begin{itemize}
				\item Spearheaded the implementation of advanced features including Rich Text Support and dynamic highlighting functionality for annotations.
				\item Reduced page load time by 80\% by consolidating data retrieval to a single API call with server-side props, utilizing \textbf{Context API} for efficient data distribution, and implementing pagination to minimize data overload.
				\item Engineered and deployed robust backend endpoints for the \textbf{Golang}-based REST API with MySQL database.
				\item Authored comprehensive tests using \textbf{Jest} and \textbf{React Testing Library} to ensure code integrity and functionality.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Software Developer Intern}{Hewlett Packard Enterprise}{May -- Aug 2023}	
			\begin{itemize}
				\item Developed and launched a \textbf{React.js}-based demo portal as the sole developer, effectively showcasing HPE GreenLake solutions and streamlining the demo process by at least 50\%.
				\item Orchestrated the automation and optimization of demo processes, utilizing \textbf{Python} and \textbf{Bash} scripts, and managed VM environments to ensure efficient and effective demo execution, reducing setup time by approximately 80\%.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Software Developer Intern}{Bolee Machine Tool Ltd.}{Apr -- Jun 2023}	
			\begin{itemize}
				\item Tackled the challenge of time-consuming manual product entries on the company's WordPress e-commerce site, previously reliant on a lengthy admin GUI process.
				\item Revolutionized product management by developing a \textbf{Python}-based automation tool using \textbf{Selenium} for the company's WordPress e-commerce site; achieved a remarkable 99\% reduction in time required for bulk price updates.
				\item Managed the company’s server system by configuring the VPN server and upgrading the storage of the NAS server.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	% \begin{cvsection}{Technical Experience}
	% 	\begin{cvsubsection}{Projects}{}{}
	% 		\begin{itemize}
	% 			\item \textbf{Instagram Clone} \href{https://github.com/pl3lee/instagram-clone}{\faGithub}. Developed an Instagram clone using Next.js, TailwindCSS, Express, Firebase Auth, MongoDB, Socket.io, and Node.js, replicating core features such as user registration, profiles, post creation, and real-time chat.
	% 			% \item \textbf{Biquadris} \href{https://github.com/pl3lee/Biquadris}{\faGithub}. Engineered a customizable Tetris variant in C++, utilizing MVC and Factory Method design patterns for a robust architecture. Created an engaging and user-friendly GUI using the X Window System, with adjustable board dimensions and win conditions.
	% 		\end{itemize}
	% 	\end{cvsubsection}
	% \end{cvsection}
	\begin{cvsection}{Projects}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
				\item \textbf{Instagram Clone} \href{https://github.com/pl3lee/instagram-clone}{\faGithub}. Developed an Instagram clone using Next.js, TailwindCSS, Express.js, MongoDB, Socket.io, and Node.js, replicating core features such as user registration, profiles, post creation, and real-time chat.
				% \item \textbf{Biquadris} \href{https://github.com/pl3lee/Biquadris}{\faGithub}. Engineered a customizable Tetris variant in C++, utilizing MVC and Factory Method design patterns for a robust architecture. Created an engaging and user-friendly GUI using the X Window System, with adjustable board dimensions and win conditions.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	% \begin{cvsection}{Additional Experience and Awards}
	% 	\begin{cvsubsection}{}{}{}	
	% 		\begin{itemize}
	% 			\item \textbf{Instructor (2003 – 2005):} Taught two full-credit Computer Science courses; average ratings of 4.8 out of 5.0.
	% 			\item \textbf{Third Prize, Senior Design Projects:} Awarded 3rd prize for Synchronized Calendar project, out of 100 projects.
	% 		\end{itemize}
	% 	\end{cvsubsection}
	% \end{cvsection}
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Waterloo, ON Canada}{University of Waterloo}{Sept 2020 -- Aug 2024}
			\begin{itemize}
				\item Honours Bachelor of Mathematics. Cumulative GPA: 88.56/100.
				\item Double Major: Computational Mathematics, and Combinatorics \& Optimization.
				\item Minor: Computer Science.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	\begin{cvsection}{Skills}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Languages:} TypeScript, JavaScript, HTML, CSS, Python, C++, Go, Bash, SQL, LaTeX, MATLAB
				\item \textbf{Technologies/Frameworks:} React, Next.js, Socket.io, Node.js, Express.js, MongoDB, PostgreSQL, MySQL, TailwindCSS, Docker, Github Actions, GitLab CI/CD pipelines, Jest, React Testing Library, Selenium, Git, Linux/Unix.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}

