\resumeSubHeadingListStart

    \resumeSubheading
      {University of Waterloo}{Waterloo, Canada}
      {Lead Developer}{Jan 2024 -- May 2024}
      \resumeItemListStart
        \resumeItem{Developed a Next.js-based web platform for a figures of speech research group, enabling user submissions and annotations of figure instances.}
        \resumeItem{Revamped the CI/CD process using GitLab pipelines, Docker, and Docker Compose, automating and accelerating testing, building, and deployment phases, and saving over 30 minutes per deployment.}
        \resumeItem{Established a robust staging environment to streamline testing and quality assurance, ensuring a more reliable and efficient development workflow.}
        \resumeItem{Hosted weekly stand-up meetings, conducted code reviews for merge requests, and set up a documentation site with a CD pipeline to ensure proper project documentation.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
   \resumeSubSubheading
    {Full Stack Developer}{Sept 2023 -- Dec 2023}
    \resumeItemListStart
       \resumeItem{Implemented advanced features including rich text support and dynamic highlighting functionality using Tiptap.}
       \resumeItem{Reduced page load time by 80\% by consolidating data retrieval to a single API call with server-side props, utilizing Context API for efficient data distribution, and implementing pagination to minimize data overload.}
       \resumeItem{Engineered and deployed robust backend endpoints for the Golang-based REST API with MySQL database.}
       \resumeItem{Authored comprehensive tests using Jest and React Testing Library to ensure code integrity and functionality.}
    \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Hewlett Packard Enterprise}{Hong Kong, China}
      {Software Developer Intern}{May 2023 -- Aug 2023}
      \resumeItemListStart
        \resumeItem{Developed and launched a React.js-based demo portal as the sole developer, effectively showcasing HPE GreenLake solutions and streamlining the demo process by at least 50\%.}
        \resumeItem{Orchestrated the automation and optimization of demo processes, utilizing Python and Bash scripts, and managed VM environments to ensure efficient and effective demo execution, reducing setup time by approximately 80\%.}
    \resumeItemListEnd

    \resumeSubheading
      {Bolee Machine Tool Ltd.}{Hong Kong, China}
      {Software Developer Intern}{Apr 2023 -- May 2023}
      \resumeItemListStart
        \resumeItem{Tackled the challenge of time-consuming manual product entries on the company’s WordPress e-commerce site, previously reliant on a lengthy admin GUI process.}
        \resumeItem{Revolutionized product management by developing a Python-based automation tool using Selenium for the company’s
        WordPress e-commerce site; achieved a 99\% reduction in time required for bulk price updates.}
        \resumeItem{Managed the company’s server system by configuring the VPN server and upgrading the storage of the NAS server.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd